\section{Portfolio}

\subsection{Context}

During our last year at INSA we had to write a Portfolio, gathering all the projects, skills that we developed during this year as well as an analysis of these different experience. As this document is part of the project and reports that we have to do during this year, it seems normal that it has its own part in the portfolio in order for me to present the skills that it made me learn as well as the critics that I have regarding this document.

\subsection{Technical Aspects}

Through the redaction of this document, I had the opportunity to reinforce communication skills that I already developed with other personal and academical experiences. As you probably noticed, this document is wrote in English. This is at the same time the main difficulty, as we are not native English speaker, and a great opportunity to develop our mastery of the language. Indeed, I had the opportunity, notably with my internship this summer in an English speaking company, to write reports in English but this portfolio is by far the longest document I had to write in another language than French. 
\\\par
As many other courses during this year, this document helped me to develop other soft skills like for example my writing skills. Indeed, for this kind of long document and spread across time, it is important to be able to summarize our thoughts to only deliver relevant information and to avoid going in too many directions. 

\subsection{Skill Matrix}

\begin{itemize}
    \item Reflect on my training process and methods
    \item Be able to put forward my training experiences, whether explicit or implicit
    \item Be self-sufficient and responsible for my training
\end{itemize}

As I will mention in the analysis part of this course, I really do not see the point of this course and I have the same feeling for the skills present in the skill matrix. Indeed, I think that some of these skills are too vague. As this course is done 100\% in autonomy, I do not think that it develop any skill except our writing, presentation skills in English as this document is in English. We also develop our ability to summarize as we need to talk about at least everything we did during this semester. The only skill present in the matrix that I find relevant and that I mastered is the reflection on my training process and methods. The two other skills are too vague especially being self-sufficient and responsible for my training. 

\subsection{Analysis}

In my opinion, this course suffers from a lot of contradiction and does not answer to any need for student. Indeed, this course is presented as a way to summarize all our projects of the year to illustrate the fact that we have various skills and in the end help for recruitment processes as it can be send to recruiters. However, for the argument of helping with recruitment processes, firstly, we cannot finish it before the end of the semester because we did not finish every courses but at that time a huge majority of the class would already have an internship. Secondly, even if we did have finish this document on time, after talking to other students in the class, everyone agreed with the fact that we would not send this document to a recruiter because: it is way too long and that nobody would ever read it and also because we are forced to discuss about topics that we do not want to talk about. Indeed, we have to talk about every course of this year even the ones that do not have anything to do with our professional project. 
\\\par
The other argument for this course is that it illustrate the fact that we have various skills which is true. However the problem is that this document is way too long and takes too much time and energy to finish. It is very frustrating for students to spend the major part of their year writing a document that only you, the teachers, would ever read. It is without exaggerating, the project that took most of my personal time, that I would have preferred spending on other technical projects. 
As only teachers from INSA read this document it feels like its only  purpose is to do some feedback about the year which is what I chose to do when writing this document. 
\\\par
To conclude on this course, I think that at the very least, it should be changed to be shorten by a lot but from a personal point of view I think that it should totally be removed from the curriculum.